---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Twenty

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

`Twenty` is an R package created by group number 20 for a school project. 

`Twenty` provides a consistent set of verbs that help you solve the most common data analysis challenges.

## Installation

### Development Version

The easiest way to get `Twenty` is to install the whole package:

You can install the development version of `Twenty` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rforbiodatascience22/Twenty")
```

If you are new to `Twenty` the best place to start is this github repository

```{r example, message=FALSE, warning=FALSE}
library(Twenty)
```

```{r eval=FALSE, warning=FALSE, include=FALSE}

# data. 
data("data_two")
my_data_two

# convert
gdl <- convert_to_long(my_data_two)


# nest
wdn <- make_nested(gdl, `Gene`)
wdn

data("wide_wide_west")
west_data_wide
  
#pca
pca_fit <- perform_pca(west_data_wide)
pca_fit 

#rotate. 
make_rotation_table(pca_fit)
```

***

## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on GitHub.
For questions and other discussion, please email `s172084@dtu.dk`

Please note that this project is released with a Contributor Code of Conduct. By participating in this project you agree to abide by its terms.
