---
title: "Twenty"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Twenty}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

`Twenty` is an R package created by group number 20 for a school project.

`Twenty` provides a consistent set of verbs that help you solve the most common data analysis challenges.

## Installation

### Development Version

The easiest way to get `Twenty` is to install the whole package:

You can install the development version of `Twenty` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rforbiodatascience22/Twenty")
```

If you are new to `Twenty` the best place to start is this github repository.

```{r example, eval=FALSE}
library(Twenty)
```

***

## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on GitHub.
For questions and other discussion, please email `s172084@dtu.dk`

Please note that this project is released with a Contributor Code of Conduct. By participating in this project you agree to abide by its terms.
